BOLD Parameter Estimation Using Particle Filters

### 2010-07-16 doc/thesis/results.tex
adjusted the results

%note to self, epsilon should probably be uniform between 0 and something
\section{Simulated Volume}
\begin{enumerate}
\item Parameter Map 
\item Error map of parameters
\item Histogram of \%errors between parameters
\item Activation Map based on a single region with high $\epsilon$, compared with linear
\end{enumerate}

Final parameter distribution among active regions.
Q-Q plots?

\section{FMRI Data}
....

>>>>

%note to self, epsilon should probably be uniform between 0 and something
\section{Simulated Volume}

\chapter{Real Data}
\begin{figure}
\label{fig:hm_canon_spm}
\subfigure[]{\label{fig:hm_spm} \includegraphics[scale=.66]{images/spm_hm}}
\subfigure[]{\label{fig:hm_canon_spm_x} \includegraphics[scale=.85]{images/spm_hm_x}}
\subfigure[]{\label{fig:hm_canon_spm_y} \includegraphics[scale=.85]{images/spm_hm_y}}
\subfigure[]{\label{fig:hm_canon_spm_z} \includegraphics[scale=.85]{images/spm_hm_z}}
\subfigure{\label{fig:scale_spm} \includegraphics[scale=.3]{images/scale1}}
\caption{Sagittal, coronal and axial slices of SPM results (\autoref{fig:hm_canon_spm_x} \autoref{fig:hm_canon_spm_y} 
         \autoref{fig:hm_canon_spm_x}), as well as a series of axial slices, \autoref{fig:hm_spm}. Units
         of activation are in Student's T-scores. Higher indicates higher assurance that the signal cannot
         have occurred through noise alone.}
\end{figure}

\begin{figure}
\label{fig:hm_canon_pfilter}
\subfigure[]{\label{fig:hm_pfilter} \includegraphics[scale=.66]{images/pfilter_hm}}
\subfigure[]{\label{fig:hm_canon_pfilter_x} \includegraphics[scale=.85]{images/pfilter_hm_x}}
\subfigure[]{\label{fig:hm_canon_pfilter_y} \includegraphics[scale=.85]{images/pfilter_hm_y}}
\subfigure[]{\label{fig:hm_canon_pfilter_z} \includegraphics[scale=.85]{images/pfilter_hm_z}}
\subfigure{\label{fig:scale_pfilter} \includegraphics[scale=.3]{images/scale2}}
\caption{Sagittal, coronal and axial slices of SPM results (\autoref{fig:hm_canon_pfilter_x} \autoref{fig:hm_canon_pfilter_y} 
         \autoref{fig:hm_canon_pfilter_x}), as well as a series of axial slices, \autoref{fig:hm_pfilter}. 
         Units of match is normalized $\sqrt{MSE}$. The lowest (best) levels were $.7$,
         whereas the worst levels could go higher than 100 (not shown).}
\end{figure}

### 2010-07-16 doc/thesis/thesis.tex
updated images, more work on background methods
done with properties I think
added quite a few plots. Should be able to write results for single voxel simulations.
adjusted the results

\documentclass{report}
\usepackage[left=3cm,top=2cm,right=3cm]{geometry}

\usepackage{times}
\usepackage[siunitx]{circuitikz}
%\usetikzlibrary{trees}
%\usetikzlibrary{shapes,snakes}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithmic}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{cancel}
\usepackage[colorlinks=true]{hyperref}

@@

\begin{document}
\title{BOLD Parameter Estimation Using Particle Filters}
\author{Micah Chambers\\Virginia Polytechnic Institute and State University}
\date{}
\maketitle

\tableofcontents

@@

\bibliographystyle{apalike}
%\bibliographystyle{abbrvnat}
%\bibliographystyle{abbrv}
\bibliography{library}

@@

%trash
%stream of new developments in modeling the BOLD signal, nothing has have been
%a plethora of new studies pushing advancements 
%the choice of analysis tools is still relatively limited. Every widely
%available analysis tool is based on parametric modeling, which requires
%prior knowledge of the noise distribution. Indeed, the linear methods
%usually applied are known not to be robust to non-gaussian, non-white
%noise, which is why so many pre-processing steps are necessary.
%These limitations cast a long shadow over any experiment that claims to be
%able to reject the null hypothesis, no matter the P-value. While obviously
%there is a correlation between the BOLD signal and actual activity, its
%possible the current parametric tests are over-estimating the actual amount
%of activity. Its also possible that the current methods underestimate
%actual activity. In this paper we propose a robust model-based approach to 
%activation detection that makes no assumptions about the underlying noise
%model.

>>>>

% PROJECT: <ETD> Electronic Thesis and Dissertation Initiative
%   TITLE: LaTeX report template for ETDs in LaTeX
%  AUTHOR: Neill Kipp, nkipp@vt.edu
%     URL: http://etd.vt.edu/latex/
% SAVE AS: etd.tex
% REVISED: September 6, 1997
% 
%\documentclass[12pt,dvips]{report}
\documentclass[12pt]{report}
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{8.5in}
\setlength{\evensidemargin}{0in}
\setlength{\oddsidemargin}{0in}
\setlength{\topmargin}{0in}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.1in}

%\usepackage[left=3cm,top=2cm,right=3cm]{geometry}

\usepackage{colortbl}
\usepackage{times}
\usepackage[siunitx]{circuitikz}
%\usetikzlibrary{trees}
%\usetikzlibrary{shapes,snakes}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{cancel}
\usepackage[colorlinks=true]{hyperref}

\usepackage{algorithm}
\numberwithin{algorithm}{chapter}
\usepackage{algorithmic}

@@

\begin{document}
\thispagestyle{empty}
\pagenumbering{roman}
\begin{center}

% TITLE
{\Large 
BOLD Parameter Estimation Using Particle Filters
}

\vfill

Micah C. Chambers

\vfill

Thesis submitted to the Faculty of the \\
Virginia Polytechnic Institute and State University \\
in partial fulfillment of the requirements for the degree of

\vfill

Master of Science \\
in \\
Electical Engineering

\vfill

Chris L. Wyatt, Chair \\
William T. Baumann\\
Aloysius. A. Beex \\
Daniel J. Stilwell

\vfill

August 10, 2010\\
Blacksburg, Virginia

\vfill

Keywords: BOLD Response, FMRI, Nonlinear Systems, Particle Filter, Bayesian Statistics
\\
Copyright 2010, Micah C. Chambers

\end{center}

\pagebreak

\thispagestyle{empty}
\begin{center}

{\large BOLD Parameter Estimation Using Particle 
Filters }

\vfill

Micah C. Chambers

\vfill

(ABSTRACT)

\vfill

\end{center}

Abstract Abstract Abstract ...

\vfill

% GRANT INFORMATION

%That this work received support from the Southeastern Universities
%Research Association (SURA) ``Monticello Library Project'' is purely
%coincidental.

\pagebreak

% Dedication and Acknowledgments are both optional
% \chapter*{Dedication}
% \chapter*{Acknowledgments}

\tableofcontents
\pagebreak

\listoffigures
\pagebreak

\listoftables
\pagebreak

\pagenumbering{arabic}
\pagestyle{myheadings}

@@

\bibliographystyle{ieeetr}
%\bibliographystyle{apalike}
%\bibliographystyle{abbrvnat}
%\bibliographystyle{abbrv}
\bibliography{library}

@@

%trash
%stream of new developments in modeling the BOLD signal, nothing has have been
%a plethora of new studies pushing advancements 
%the choice of analysis tools is still relatively limited. Every widely
%available analysis tool is based on parametric modeling, which requires
%prior knowledge of the noise distribution. Indeed, the linear methods
%usually applied are known not to be robust to non-gaussian, non-white
%noise, which is why so many pre-processing steps are necessary.
%These limitations cast a long shadow over any experiment that claims to be
%able to reject the null hypothesis, no matter the P-value. While obviously
%there is a correlation between the BOLD signal and actual activity, its
%possible the current parametric tests are over-estimating the actual amount
%of activity. Its also possible that the current methods underestimate
%actual activity. In this paper we propose a robust model-based approach to 
%activation detection that makes no assumptions about the underlying noise
%model.
%

%\chapter{Introduction}
%\markright{Albert J. Kippleby \hfill Chapter 1. Introduction \hfill}
%
%William Shakespeare has profoundly affected the field of literature
%worldwide.  In the United States there was a surge of Shakespearean
%literature starting in the 1960s, with the opening of the Montgomery
%Shakespearean festival and continuing into the present ...

%%%%%%%%%%%%%%%%%
%
% Include an EPS figure with this command:
%   \epsffile{filename.eps}
%

%%%%%%%%%%%%%%%%
%
% Do tables like this:

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%
%% PROJECT: <ETD> Electronic Thesis and Dissertation Initiative
%%   TITLE: LaTeX report template for ETDs in LaTeX
%%  AUTHOR: Neill Kipp, nkipp@vt.edu
%%     URL: http://etd.vt.edu/latex/
%% SAVE AS: etd.tex
%% REVISED: September 6, 1997
%% 
%
%% Instructions: Remove the data from this document and replace it with your own,
%% keeping the style and formatting information intact.  More instructions
%% appear on the Web site listed above.
%
%\documentclass[12pt,dvips]{report}
%
%\setlength{\textwidth}{6.5in}
%\setlength{\textheight}{8.5in}
%\setlength{\evensidemargin}{0in}
%\setlength{\oddsidemargin}{0in}
%\setlength{\topmargin}{0in}
%
%\setlength{\parindent}{0pt}
%\setlength{\parskip}{0.1in}
%
%% Uncomment for double-spaced document.
%% \renewcommand{\baselinestretch}{2}
%
%% \usepackage{epsf}
%
%\begin{document}
%
%\thispagestyle{empty}
%\pagenumbering{roman}
%\begin{center}
%
%% TITLE
%{\Large 
%Use of Metaphor in Shakespeare's Plays and its Potential
%Application in Twenty-first Century Literature
%}
%
%\vfill
%
%Albert J. Kippleby
%
%\vfill
%
%Dissertation submitted to the Faculty of the \\
%Virginia Polytechnic Institute and State University \\
%in partial fulfillment of the requirements for the degree of
%
%\vfill
%
%Doctor of Philosophy \\
%in \\
%Literature and Technology
%
%\vfill
%
%Neill A. Kipp, Chair \\
%Emilio J. Arce \\
%Scott A. Guyer \\
%Laura Weiss
%
%\vfill
%
%July 16, 1997 \\
%Blacksburg, Virginia
%
%\vfill
%
%Keywords: Metaphysics, Information Retrieval, Spacecraft
%\\
%Copyright 1997, Albert J. Kippleby
%
%\end{center}
%
%\pagebreak
%
%\thispagestyle{empty}
%\begin{center}
%
%{\large Use of Metaphor in Shekespeare's Plays and its Potential
%Application in Twenty-first Century Literature}
%
%\vfill
%
%Albert J. Kippleby
%
%\vfill
%
%(ABSTRACT)
%
%\vfill
%
%\end{center}
%
%The need for concrete examples increases when technology becomes
%difficult to explain.  In documentation for computer systems
%especially, we see a wide audience of field experts attempting to
%comprehend documentation for computer software and hardware of which
%they should only require a cursory understanding.  Additionally, as
%the pace of the information age quickens we see document authors
%struggle for \textit{examplia-concretes} with wide applicability, and
%consistently rely on excerpts from Shakespearean literature as a
%public-domain source for their various explications.
%
%We predict the twenty-first century will be no different.  Actuarial
%studies show explosion in the information industry such that four out
%of five persons will be \textit{bona fide} electronic document
%authors; many of those will have one or more college degrees.  We
%prove through computer simulation \textsc{Machinum Simitatores} that
%authors of twenty-first century literature will be affected by these
%examples and will include metaphor with Shakespearean source into
%their writing with increasing frequency.
%
%\vfill
%
%% GRANT INFORMATION
%
%That this work received support from the Southeastern Universities
%Research Association (SURA) ``Monticello Library Project'' is purely
%coincidental.
%
%\pagebreak
%
%% Dedication and Acknowledgments are both optional
%% \chapter*{Dedication}
%% \chapter*{Acknowledgments}
%
%\tableofcontents
%\pagebreak
%
%\listoffigures
%\pagebreak
%
%\listoftables
%\pagebreak
%
%\pagenumbering{arabic}
%\pagestyle{myheadings}
%
%\chapter{Introduction}
%\markright{Albert J. Kippleby \hfill Chapter 1. Introduction \hfill}
%
%William Shakespeare has profoundly affected the field of literature
%worldwide.  In the United States there was a surge of Shakespearean
%literature starting in the 1960s, with the opening of the Montgomery
%Shakespearean festival and continuing into the present ...
%
%%%%%%%%%%%%%%%%%%
%%
%% Include an EPS figure with this command:
%%   \epsffile{filename.eps}
%%
%
%%%%%%%%%%%%%%%%%
%%
%% Do tables like this:
%
% \begin{table}
% \caption{The Graduate School wants captions above the tables.}
%\begin{center}
% \begin{tabular}{ccc}
% x & 1 & 2 \\ \hline
% 1 & 1 & 2 \\
% 2 & 2 & 4 \\ \hline
% \end{tabular}
%\end{center}
% \end{table}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%% If you are using BibTeX, uncomment the following:
%% \thebibliography
%%
%% Otherwise, uncomment the following:
%% \chapter*{Bibliography}
%
%% \appendix
%
%% In LaTeX, each appendix is a "chapter"
%% \chapter{Program Source}
%
%
%% Finally, the VITA
%\chapter*{Vita}
%
%Albert was born on a sunny day...
%
%\end{document}
